Figures main manuscript

### 2019-12-13 code/05_figures-and-correlations.rmd
Updated heterogeneity sub-analysis when MA ES = 0

#1. Standardized mean differences----
SMDs <- tau_per_type %>% filter(effect_type == "Standardized Mean Difference")

@@

##When effect size == 0, what is average heterogeneity?
mean(SMDs$tau[SMDs$eff_size < 0.05]) #for tau = 0.016
mean(SMDs$s_I2[SMDs$eff_size < 0.05]) #I2 = 3.05
mean(SMDs$H2[SMDs$eff_size < 0.05]) #H2 = 0.88

@@

>>>>

#1. Standardized mean differences----
SMDs <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
  filter(effect_type == "Standardized Mean Difference")

@@

@@

#1.05 When ES not sig. diff from zero----
##When effect size not sig diff from 0 (alpha = .05), what is average heterogeneity?
nrow(SMDs[SMDs$eff_size_p > 0.05,]) #20/40 SMDs have ES not sig. diff from zero
sum(SMDs$tau[SMDs$eff_size_p > 0.05] == 0) #13/20 of these have taus == 0

mean(SMDs$tau[SMDs$eff_size_p > 0.05]) #for tau = 0.017
mean(SMDs$s_I2[SMDs$eff_size_p > 0.05]) #I2 = 3.49
mean(SMDs$H2[SMDs$eff_size_p > 0.05]) #H2 = 0.89

SMDs_not_sig <- SMDs[SMDs$eff_size_p > 0.05,]$effect

dat %>% filter(effect %in% SMDs_not_sig) %>% #amongst the non-sig SMDS
  group_by(effect) %>% 
  summarize(K = n()) %>% #compute number of labs (K) per effect
  ungroup() %>% 
  summarize(mean_k = mean(K), #average number of K = 32.8
            median = quantile(K)['50%']) #median 22.5

#% estimates that should be non-zero under central chi-square distribution. For I2 any effect size where Q <= DF ->  I2 zero
pchisq(23, 23, lower.tail = FALSE)

#logs
logOR <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
  filter(effect_type == "Log Odds Ratio")

nrow(logOR[logOR$eff_size_p > 0.05,]) #only 1 log odds ratio not signifcant
